The Geometry of Archaeological Thought: Analysing discplinary change using word embeddings from conference abstracts

### 2020-05-14 documents/paper.Rmd
cminor edit on method

The PDFs for the years 1962-1994 contain images of pages, and after 2005 the PDFs are searchable text. We converted the page images from PDF to PNG files using ImageMagick software, and then used optical character recognition to extract text from the PNG files with the Tesseract package [@Kay2007]. We obtained an acceptable rate of 95-98% word-level OCR accuracy across the PDFs [@Holley2009]. After OCR, we used the quanteda package  [@Benoit2018] to remove punctuation, numbers, and stopwords, such as "the", "an", "a", with little or no semantic meanings.

>>>>

The PDFs for the years 1962-1994 contain images of pages, and after 2005 the PDFs are searchable text. We converted the page images from PDF to PNG files using ImageMagick software, and then used optical character recognition to extract text from the PNG files with the Tesseract package [@Kay2007]. We obtained an acceptable rate of 95-98% word-level OCR accuracy across the PDFs [@Holley2009]. After OCR, we used the quanteda package  [@Benoit2018] to remove punctuation, numbers, and stopwords, such as "the", "an", "a", due to their little or no semantic meanings.
